{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-07-19 thesis/tm.tex
rerun all -X -A -S tests bc of causality violation

			& 2,1	&\cpu{10.48}&\wtm{3.22}&\ints{2}&\cpu{*2.98}&\wtm{*2.98}&\ints{2}& \ETA{8} \\

@@

			& 9,9	&\cpu{37.41}&\wtm{9.96}&\ints{2}&\cpu{*4.93}&\wtm{*4.93}&\ints{2}& \ETA{inf} \\

@@

Table~\ref{tab:verifs2} shows the new resulting levels of verification
Landslide reached before the same 10-hour timeout.
Provided that one trusts the {\tt lock} tests correctly check the desired properties,
and that open-coding hadn't introduced any new bugs (such as Figure~\ref{fig:avlbug}'s),
the benefit is clear:
the data structure tests suddenly reach unprecedented thread/iteration counts with ease,
their state space growth now defined only by their internal conflicts from tree rebalancing, map resizing, and so on.
In total,
summing the testing times of {\tt lock}({\tt mutex})$(K,N)$ and {\tt avl\_mutex}$(K,N)$
produces the same verification as {\tt avl\_fixed}$(K,N)$ far more cheaply.
Furthermore, {\tt lock}'s verification can be reused,
whereas {\tt avl\_fixed} and {\tt map\_basic} effectively duplicated the mutex verification between them.
Note also the impact that fixing Figure~\ref{fig:spinlockbug}'s performance bug
(changing a read+write to a read only)
had on even the correctness tests:
{\tt lock}({\tt spin\_fixed})'s state spaces were reduced by more than half compared to {\tt lock}({\tt spinlock}).

@@

			& 2,1 & \cpu{14.23} & \ints{41} \\

@@

			& 2,2 & \cpu{4944.37} & \ints{38544} \\

@@

			& 3,1 & \cpu{13649.32} & \ints{97462} \\

@@

			& 2,1 & \cpu{12.26} & \ints{31} \\

@@

			& 2,2 & \cpu{1662.21} & \ints{15076} \\
			& 2,3 & \ETAdag{3d 20h} & \ETAdag{2003906} \\
			& 3,1 & \cpu{2488.95} & \ints{24970} \\
			& 3,2 & \ETAdag{207d 20h} & \ETAdag{6514618} \\

@@

			& 2,1 & \cpu{9.42} & \ints{22}	\\

@@

			& 2,2 & \cpu{44.07} & \ints{1208}	\\
			& 2,3 & \cpu{2647.38} & \ints{71136}	\\
			& 2,4 & \ETAdag{2d 1h} & \ETAdag{3223055}	\\
			& 3,1 & \cpu{42.11} & \ints{1148}	\\
			& 3,2 & \ETAdag{11d 4h} & \ETAdag{4793666}	\\
			& 4,1 & \cpu{5586.37} & \ints{159664}	\\

@@

			& 2,1 & \cpu{2.96} & \ints{1}	\\

@@

			& 9,9 & \cpu{4.33} & \ints{1}	\\

@@

			& 2,1 & \cpu{3.05} & \ints{1}	\\

@@

			& 9,9 & \cpu{4.38} & \ints{1}	\\

>>>>

			& 2,1	&\cpu{8.17}&\wtm{2.65}&\ints{2}&\cpu{*2.39}&\wtm{*2.39}&\ints{2}& \ETA{4} \\

@@

			& 9,9	&\cpu{36.64}&\wtm{9.78}&\ints{2}&\cpu{*4.75}&\wtm{*4.75}&\ints{2}& \ETA{inf} \\

@@

Table~\ref{tab:verifs2} shows the new resulting levels of verification
Landslide reached before the same 10-hour timeout.
Provided that one trusts the {\tt lock} tests correctly check the desired properties,
and that open-coding hadn't introduced any new bugs (such as Figure~\ref{fig:avlbug}'s),
the benefit is clear:
the data structure tests suddenly reach unprecedented thread/iteration counts with ease,
their state space growth now defined only by their internal conflicts from tree rebalancing, map resizing, and so on.
In total,
summing the testing times of {\tt lock}({\tt mutex})$(K,N)$ and {\tt avl\_mutex}$(K,N)$
produces the same verification as {\tt avl\_fixed}$(K,N)$ far more cheaply.
Furthermore, {\tt lock}'s verification can be reused,
whereas {\tt avl\_fixed} and {\tt map\_basic} effectively duplicated the mutex verification between them.

Note two curiosities:
firstly,
the impact that fixing Figure~\ref{fig:spinlockbug}'s performance bug
(changing a read+write to a read only)
had on even the correctness tests:
{\tt lock}({\tt spin\_fixed})'s state spaces were reduced by more than half compared to {\tt lock}({\tt spinlock}).
Secondly, {\tt spinlock} and {\tt spin\_fixed} take longer to test per interleaving
(CPU time divided by state space size)
than {\tt mutex},
because while {\tt mutex} abstracts away threads needing to wait their turn for the critical section
behind an API Landslide understands,
the spinlock's wait loop is open-coded, and Landslide must fall back on its costlier heuristic synchronization detection
(\sect{\ref{sec:landslide-blocking}}).
In this way (and also, of course, because {\tt mutex}'s state spaces are smaller overall),
{\tt mutex} can be seen in turn as a further abstraction reduction of {\tt spinlock}.

@@

			& 2,1 & \cpu{2.49} & \ints{4} \\ % certified causality ok

@@

			& 2,2 & \cpu{174.26} & \ints{1702} \\ % certified causality ok

@@

			& 3,1 & \cpu{26.97} & \ints{246} \\ % certified causality ok

@@

			& 2,1 & \cpu{2.47} & \ints{4} \\ % certified causality ok

@@

			& 2,2 & \cpu{94.64} & \ints{998} \\ % certified causality ok
			& 2,3 & \ETAdag{todo} & \ETAdag{todo} \\
			& 3,1 & \cpu{218.02} & \ints{185} \\ % certified causality ok
			& 3,2 & \ETAdag{todo} & \ETAdag{todo} \\

@@

			& 2,1 & \cpu{2.49} & \ints{4}		\\ % certified causality ok

@@

			& 2,2 & \cpu{12.72} & \ints{180}	\\ % certified causality ok
			& 2,3 & \cpu{273.45} & \ints{8356}	\\ % certified causality ok
			& 2,4 & \ETAdag{todo} & \ETAdag{todo}	\\
			& 3,1 & \cpu{11.21} & \ints{132}	\\ % certified causality ok
			& 3,2 & \ETAdag{todo} & \ETAdag{todo}	\\
			& 4,1 & \cpu{493.38} & \ints{15064}	\\ % certified causality ok
			& 4,2 & \\ % TODO maybe?????? well its 10hrs

@@

			& 2,1 & \cpu{2.42} & \ints{1}	\\

@@

			& 9,9 & \cpu{3.69} & \ints{1}	\\

@@

			& 2,1 & \cpu{2.35} & \ints{1}	\\

@@

			& 9,9 & \cpu{3.79} & \ints{1}	\\
